---
title: "Homework 6"
author: "Margaret Gacheru"
date: "November 21, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

#Problem 1

This dataset contains information on homicides in 50 large ctiies across the country.

```{r warning = FALSE, message = FALSE}
url = "https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"
homicide_data = read_csv(url)

```


Create a city_state variable (e.g. "Baltimore, MD"), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO - these don't report victim race. Also omit Tulsa, AL - this is a data entry mistake. Modifiy victim_race to have categories white and non-white , with white as the reference category. Be sure that victim_age is numeric. 

```{r}
tidy_homicide_data = 
  homicide_data%>%
  mutate(city_state = str_c(city, ", ", state))%>%
  select(city_state, everything())%>%
  filter(!city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL"))%>%
  mutate(victim_race = ifelse(victim_race == "White", "White", "Non-white"),
         victim_race = forcats::fct_relevel(victim_race, c("White", "Non-white")),
         victim_age = as.numeric(victim_age),
         crime_status = ifelse(disposition == "Closed by arrest", 1, 0))

```

For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race (as just defined) as predictors. Save the output of glm as an R object; apply the broom::tidy to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims keeping all other variables fixed. 

```{r}

glm_output_md = tidy_homicide_data%>%
  filter(city_state == "Baltimore, MD")%>%
  glm(crime_status ~ victim_age + victim_sex + victim_race, family = binomial(link = "logit"), data = .)%>%
  broom::tidy()%>%
  mutate(conf.low = exp(estimate - 1.96*(std.error)),
         conf.high = exp(estimate + 1.96*(std.error)),
         estimate = exp(estimate))%>%
  select(term, estimate, conf.low, conf.high)%>%
  filter(term == "victim_raceNon-white")%>%
  mutate(term = str_replace(term, "victim_race", "Race: "))

glm_output_md
  
```

Intepretation: In this study, subjects with hypertension (reference group) 2.71 times the odds of developing cardiovascular disease compared to non-hypertensive subjects. With 95% conficence the true odds ratio lies in the range of 2.26-3.24.


Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing non-white victims to white victims. Do this within a "tidy" pipeline, making use of purrr::map , list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city.

```{r}

glm_output = tidy_homicide_data%>%
  nest(uid:crime_status)%>%
  mutate(models = map(data, ~glm(crime_status ~ victim_age + victim_sex + victim_race, family = binomial(link = "logit"), data = .x)),
         models = map(models, broom::tidy))%>%
  select(-data)%>%
  unnest()%>%
  filter(term == "victim_raceNon-white")%>%
  mutate(conf.low = exp(estimate - 1.96*(std.error)),
         conf.high = exp(estimate + 1.96*(std.error)),
         estimate = exp(estimate))%>%
  select(city_state, term, estimate, conf.low, conf.high)%>%
  mutate(term = str_replace(term, "victim_race", "Race: "))

glm_output
  
```

Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.

```{r}

glm_output%>%
  ggplot(aes(reorder(city_state, estimate), estimate, color = city_state))+
  geom_point()+
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high))+
  labs(
    y = "Adjusted Odds Ratio",
    x = "City, State",
    title = "Odds Ratio for Solving Homicides Comparing Non-white to White Victims")+
  viridis::scale_color_viridis(discrete = TRUE)+
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 90, hjust = 1))

```


#Problem 2


Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.). 

```{r}

birthweight_data = read_csv("./data/birthweight.csv")

birthweight_data = birthweight_data%>%
  mutate(babysex = as.factor(babysex),
         frace = as.factor(frace),
         malform = as.factor(malform),
         mrace = as.factor(mrace))

summary(birthweight_data)
```

The variables pnumsga and pnumlbw have all entries equal to 0

Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values - use add_predictions and add_residuals in making this plot. 

As a starting point, we can fit the preliminary model based on factors that are believed to have an influence in low birth weights. 

```{r}

modified_birthweight_data = birthweight_data%>%
  mutate(babysex_male = ifelse(babysex == "1", "1", "0"),
         frace_black = ifelse(frace == "2", "1", "0"),
         mrace_black = ifelse(mrace == "2", "1", "0"))

fit = lm(bwt ~ bhead + blength + babysex_male + delwt  + frace_black + mrace_black + fincome + gaweeks + malform + mheight + momage + parity + ppbmi + smoken + wtgain, data = modified_birthweight_data)

summary(fit)

```


Use criterion based procedures to determine the best model from the subset of variables 

```{r}

best <- function(model, ...) 
{
  subsets <- regsubsets(formula(model), model.frame(model), ...)
  subsets <- with(summary(subsets),
                  cbind(p = as.numeric(rownames(which)), which, rss, rsq, adjr2, cp, bic))
  
  return(subsets)
}  


# Select the 'best' model of all subsets for 4-predictor model
round(best(fit, nbest = 1),2)
```

We are left with a model with baby's head circumference, baby's length at birth, baby's sex, mother's race (black or not), mother's weight at delivery, gestational age, mother's pre-pregnancy BMI, and average number of cigarettes smoked per day during pregnancy as the main effects.  

Compare your model to two others: One using length at birth and gestational age as predictors (main effects only): One using head circumference, length, sex, and all interactions (including the three-way interaction) between these, Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate. 

```{r}

```

