---
title: "Homework 6"
author: "Margaret Gacheru"
date: "November 21, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

#Problem 1

This dataset contains information on homicides in 50 large ctiies across the country.

```{r warning = FALSE, message = FALSE}
url = "https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"
homicide_data = read_csv(url)

```


Create a city_state variable (e.g. "Baltimore, MD"), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO - these don't report victim race. Also omit Tulsa, AL - this is a data entry mistake. Modifiy victim_race to have categories white and non-white , with white as the reference category. Be sure that victim_age is numeric. 

```{r}

```

For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race (as just defined) as predictors. Save the output of glm as an R object; apply the broom::tidy to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims keeping all other variables fixed. 

```{r}

```

Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing non-white victims to white victims. Do this within a "tidy" pipeline, making use of purrr::map , list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city.

```{r}

```

Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.

```{r}

```


#Problem 2


Load and clean the data for regression analysis (i.e.?convert numeric to factor where appropriate, check for missing data, etc.). 

```{r}

```


Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values - use add_predictions and add_residuals in making this plot. 

```{r}

```


Compare your model to two others: One using length at birth and gestational age as predictors (main effects only): One using head circumference, length, sex, and all interactions (including the three-way interaction) between these, Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate. 

```{r}

```

